Accounting for Fiber Collisions in the Galaxy Power Spectrum Measurements

### 2015-12-16 fc_paper/fc_paper.tex
restructuring the new paper

We present two methods to account for fiber collisions in the power spectrum. The first method statistically reconstructs the clustering of fiber collided galaxy pairs by modeling the distribution of the line-of-sight displacement between them using cases where both redshifts are obtained. The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator. For the monopole, this method reproduces the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$ -- a significant improvement from existing correction methods, especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$). In our second method, we model the effect of fiber collisions on the true galaxy power spectrum by Fourier transforming an analytical estimate of the effect of fiber collisions on the two-point correlation function. Using this method we are able to reproduce the power spectrum quadrupole with fiber collisions from the true power spectrum to within sample variance for $k < 0.6\;h/\mathrm{Mpc}$ ({\bf MADEUPNUMBER}). {\bf INCLUDE MORE NUMBERS}. With statistical uncertainty no longer dominating galaxy clustering measurements, the methods we present in accounting for fiber collisions will allow us to extend power spectrum measurements to smaller scales than previous possible.

%We present our fiber collision correction method for the power spectrum monopole, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we successfully reproduce the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$. Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data. 
\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

@@

In Section \ref{sec:catalog}, we briefly describe the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper. We demonstrate the effects of fiber collisions on power spectrum measurements and compare correction methods in the literature in Section \ref{sec:fc_corr}. Afterwards we present our two methods of accounting for fiber collisions and then in Section \ref{sec:results} apply the methods to the mock catalogs. Finally in Section \ref{sec:summary} we summarize and discuss our results.

@@

\def \cmasscolor{black}
\def \ldgcolor{blue}
\def \qpmcolor{orange}
\def \tmcolor{green}
\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{fcpaper_z_dist.png} \label{fig:zdist}
\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor). Bin size of $\Delta z = 0.025$ was used to compute the each of the distributions. LasDamas mock catalog has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample. QPM and Tiling Mock catalogs, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Powerspectrum Estimator
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Power Spectrum Estimator} \label{sec:pk_est}
In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements, more specifically the monopole and quadrupole of the power spectrum. Throughout the paper, when we measure the power spectrum we use the estimator described in \cite{Scoccimarro:2015aa} and the formalism therein. To reiterate Section III. A. in \cite{Scoccimarro:2015aa}, we calculate the monopole component of the power spectrum using: 
\begin{equation}\label{eq:roman_p0k}
\widehat{P_0}(k) = \frac{1}{I_{22}} \left[ \int \frac{d\Omega_k}{4 \pi} |F_0({\bf k})|^2 - N_0 \right]
\end{equation}
where 
\begin{equation}
F_0({\bf k}) = \left( \sum_{j = 1}^{N_g} - \alpha \sum_{j=1}^{N_r} \right) w_j\;e^{i {\bf k}\cdot{\bf x}_j}
\end{equation}
with standard normalization constant
\begin{equation} \label{eq:i22}
I_{22} = \alpha \sum^{N_g}_{j=1} \bar{n}({\bf x}_j)w_j^2
\end{equation}
and shot noise term
\begin{equation} \label{eq:roman_shotnoise}
N_0 = \left( \sum_{j = 1}^{N_g} - \alpha^2 \sum_{j=1}^{N_r} \right) w_j^2. 
\end{equation}
$N_0$ represents the constant shot noise contribution to the power due to the discrete density field of our galaxies. $\alpha$ is the ratio of the number of galaxies ($N_g$) over the number of synthetic random galaxies ($N_r$), $\bar{n}({\bf x})$ is the mean density of the galaxies at position ${\bf x}$, and $w_j$ is weight of each object, which includes the the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf x}_j) = \frac{1}{1+\bar{n}({\bf x}_j) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$. We note that the shot noise term in Eq. \ref{eq:roman_shotnoise} differs from the standard shot noise term from \cite{Feldman:1994aa}, which uses $N_0^\mathrm{FKP} = \alpha (1+\alpha) \sum^{N_r}_{j=1} w_j^2. $The difference between shot noise formulations will be discussed further in Section \ref{sec:shotnoise}.

@@

% P(k) plot for mocks and BOSS
\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{fcpaper_pk_comp.png} 
\caption{Average power spectrum monopole $\overline{P_0(k)}$ and quadrupole $\overline{P_2(k)}$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the estimator from \cite{Scoccimarro:2015aa}. The width of the $P_{l}(k)$ for LasDamas and QPM represent the sample variance ($\Delta P_{l}(k)$) calculated from the realizations of the mock catalogs. We emphasize that fiber collisions were not applied to the mock catalogs for the measurements above. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P_l(k)$ measurements. We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
\end{center}
\end{figure}

@@

We also plot the $P_0(k)$ and $P_2(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}. For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber collisions. Each galaxy has a statistical weight determined by, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation} 
(\citealt{Anderson:2012aa, Beutler:2014aa}), which are included in the object weights $w_j$ along with $w_{j, \mathrm{FKP}}$. The statistical weights are also included in the factor $\alpha$. So for the BOSS $P_0(k)$ and $P_2(k)$ calculations, $w_j = w_{j, \mathrm{tot}} \times w_{j, \mathrm{FKP}}$ and $\alpha' = \sum_{j=1}^{N_g} w_\mathrm{tot} / N_r$.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute the $d_{\mathrm{LOS}}$ distributions. The $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above). We focus on the peak of the distribution $-20 \; \mathrm{Mpc} < d_\mathrm{LOS} < 20 \;\mathrm{Mpc}$ (discussed in \ref{sec:dlos}).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% fiber collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{fiber collision Correction Method} \label{sec:fc_corr}
As mentioned above, a common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}). For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor. This method assumes that all galaxies within the angular fiber collision scale ($< 62 "$ for BOSS) are correlated with one another. In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one and placing it on top of the other does not significantly alter the clustering statistics. One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position. For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$. Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements, which as we present in Section \ref{sec:dlos}, are significant.

Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance. We present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between fiber-collided pairs. Then in Section \ref{sec:shotnoise}, we present modifications to the FKP power spectrum estimator in order to properly account for fiber collisions through the shot-noise correction term in the estimator.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LOS DISPLACEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
It is impossible to determine from observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are correlated or chance alignments. Fortunately, using the fiber-collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber-collided pairs and the fraction of galaxy pairs that are corrected and uncorrelated.

For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated. All redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$). So for a fiber-collided pair, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies, while the other has $w_\mathrm{fc} = 0$. Nonetheless, with redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better correct for fiber collisions.

To determine whether or not fiber-collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber-collided galaxy pairs. We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts: 
\begin{equation}
d_{\mathrm{LOS}} = D_{\mathrm{C}} (z_1) - D_{\mathrm{C}} (z_2). 
\end{equation}
$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the galaxies in the fiber-collided pair.

After calculating the $d_{\mathrm{LOS}}$ for every fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor). All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}). For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber-colldied pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.

Galaxies within the same halo, due to their gravitational interactions at halo-scales, are more likely to be in close angular proximity with each other. These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution. While the ``tail" component is composed of chance alignment galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.

Focusing on the peak of the distribution, we note that it closely traces an Gaussian function. Therefore, we fit a Gaussian of the form, 
\begin{equation} \label{eq:peak} 
p(d_{\mathrm{LOS}}) = A \; e^{-{d_{\mathrm{LOS}}^2}/{2\sigma^2}}
\end{equation}
 for a mathematical prescription of the $d_{\mathrm{LOS}}$ distribution peak as a function of the displacement for each of the data catalogs in Figure \ref{fig:d_los}. The best-fit $\sigma$ and $A$ parameters are obtained by fitting Equation \ref{eq:peak} to the $d_{\mathrm{LOS}}$ distribution peaks using MPFIT (\citealt{Markwardt:2009aa}). We list the values of $\sigma$ obtained for the mock catalogs in Table \ref{tab:mpfit}. Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogs closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogs in our investigation of fiber collisions.

 \begin{table} 
 \caption{$d_{\mathrm{LOS}}$ Distribution Best-fit Parameters} \label{tab:mpfit}
 \begin{spacing}{1.5}
 \begin{center}
 \leavevmode
 \begin{tabular}{ccc} \hline \hline
catalog &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
LasDamas 	& 6.85	& 0.71 \\ 
QPM 		& 4.98	& 0.65 \\ 
Tiling Mock 	& 5.38	& 0.57 \\ 
BOSS DR12 	& 7.6		& 0.65 \\ \hline
\end{tabular} \par
\end{center}
\end{spacing}
%    \bigskip 
{\bf Notes}: Best-fit parameter $\sigma$ and peak fraction $f_{\mathrm{peak}}$ for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
\end{table}

>>>>

We present two methods to account for fiber collisions in the power spectrum. The first method statistically reconstructs the clustering of fiber collided galaxy pairs by modeling the distribution of the line-of-sight displacements between them using cases where both redshifts are obtained. The method properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator. For the monopole, this method reproduces the true power spectrum for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$ -- a significant improvement from existing correction methods, especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$). In our second method, we model the effect of fiber collisions on the true galaxy power spectrum by Fourier transforming an analytical estimate of the effect of fiber collisions on the two-point correlation function. Using this method we are able to reproduce the power spectrum quadrupole with fiber collisions from the true power spectrum to within sample variance for $k < 0.6\;h/\mathrm{Mpc}$ ({\bf MADEUPNUMBER}). {\bf INCLUDE MORE NUMBERS}. With statistical uncertainty no longer dominating galaxy clustering measurements, the methods we present in accounting for fiber collisions will allow us to extend power spectrum measurements to smaller scales than previous possible.

%We present our fiber collision correction method for the power spectrum monopole, which first statistically reconstructs the clustering of fiber-collided pairs by modeling the distribution of the line-of-sight displacements between them, and then properly accounts for fiber collisions in the shot-noise correction term of the power spectrum estimator. Using our method, we successfully reproduce the true power spectrum monopole for the mock catalogs with residuals of $< 1\%$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ and $< 10\%$ at $k \sim 0.8 \; h/\mathrm{Mpc}$. Our comparisons to other correction methods demonstrate that our method most accurately reconstructs the true power spectrum from fiber-collided galaxy data especially at small scales ($k > 0.1\; h/\mathrm{Mpc}$), with the added advantage that our method can be validated and calibrated in observed data.

\end{abstract}
\keywords{cosmology: observations -- cosmology: large-scale structure of universe -- galaxies: distances and redshift -- galaxies: halos -- galaxies: statistics}

@@

In Section \ref{sec:catalog}, we briefly describe the simulated mock catalogs with realistically applied fiber collisions and the power spectrum estimator used throughout the paper. We demonstrate the effects of fiber collisions on power spectrum measurements and how the nearest neighbor method does not adequately account for fiber collisions at small scales in Section \ref{sec:fc_pk}. We then present our two methods of accounting for fiber collisions in Section \ref{sec:dlospeak} and Section \ref{sec:fourier} respectively. We then apply our methods to the mock catalogs and compare correction methods in the literature in Section \ref{sec:results}. Finally in Section \ref{sec:summary} we summarize and discuss our results.

@@

\def \cmasscolor{black}
\def \ldgcolor{blue}
\def \qpmcolor{orange}
\def \tmcolor{green}

% FIGURE %%%%%%
\begin{figure}
\begin{center}
\includegraphics[scale=0.35]{mock_catalog_z_dist} \label{fig:zdist}
\caption{Normalized galaxy redshift distribution for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized redshift distribution of BOSS DR12 CMASS is also plotted (\cmasscolor). Bin size of $\Delta z = 0.025$ was used to compute the each of the distributions. LasDamas mock catalog has a constant number density of galaxies throughout $0.16 < z < 0.44$, the redshift range of SDSS LRG sample. QPM and Tiling Mock catalogs, on the other hand, trace the BOSS CMASS redshift distribution ($0.43 < z < 0.7$).}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure}

@@

% P(k) plot for mocks and BOSS ---------------------------------------------------------------------------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[scale=0.5]{mock_catalog_Plk.png} 
\caption{Average power spectrum monopole $\overline{P_0(k)}$ and quadrupole $|\overline{P_2(k)}|$ for BOSS DR12 (black) and the mock catalogs LasDamas (blue), QPM (orange), Nseries (red), and Tiling Mock (green), listed in Section \ref{sec:catalog} using the estimator from \cite{Scoccimarro:2015aa}. The width of the $P_{l}(k)$ for LasDamas and QPM represent the sample variance ($\Delta P_{l}(k)$) calculated from the realizations of the mock catalogs. For $l = 2$, we plot the absolute value of $P_2(k)$ because $P_2(k) < 0$ for $k \gtrsim 0.35\;h/\mathrm{Mpc}$. We emphasize that fiber collisions were not applied to the mock catalogs for the measurements above. Meanwhile, galaxy weights (Equation \ref{eq:weight}) are applied to the BOSS DR12 $P_l(k)$ measurements. We remind readers that the LasDamas mock catalog has an overall greater $\overline{P(k)}$ due to the fact that the catalog spans the SDSS LRG sample redshift range instead of the BOSS redshift range of the other mock catalogs.} \label{fig:mockpk}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Powerspectrum Estimator
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Power Spectrum Estimator} \label{sec:pk_est}

In this paper, we focus on the effects of fiber collisions on the galaxy power spectrum out of the other clustering measurements, more specifically the monopole and quadrupole of the power spectrum. Throughout the paper, when we measure the power spectrum we use the estimator described in \cite{Scoccimarro:2015aa} and the formalism therein. To reiterate Section III. A. in \cite{Scoccimarro:2015aa}, we calculate the monopole component of the power spectrum using: 
\begin{equation}\label{eq:roman_p0k}
\widehat{P_0}(k) = \frac{1}{I_{22}} \left[ \int \frac{d\Omega_k}{4 \pi} |F_0({\bf k})|^2 - N_0 \right]
\end{equation}
where 
\begin{equation}
F_0({\bf k}) = \left( \sum_{j = 1}^{N_g} - \alpha \sum_{j=1}^{N_r} \right) w_j\;e^{i {\bf k}\cdot{\bf x}_j}
\end{equation}
with standard normalization constant
\begin{equation} \label{eq:i22}
I_{22} = \alpha \sum^{N_g}_{j=1} \bar{n}({\bf x}_j)w_j^2
\end{equation}
and shot noise term
\begin{equation} \label{eq:roman_shotnoise}
N_0 = \left( \sum_{j = 1}^{N_g} - \alpha^2 \sum_{j=1}^{N_r} \right) w_j^2. 
\end{equation}
$N_0$ represents the constant shot noise contribution to the power due to the discrete density field of our galaxies. $\alpha$ is the ratio of the number of galaxies ($N_g$) over the number of synthetic random galaxies ($N_r$), $\bar{n}({\bf x})$ is the mean density of the galaxies at position ${\bf x}$, and $w_j$ is weight of each object, which includes the the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf x}_j) = \frac{1}{1+\bar{n}({\bf x}_j) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$. We note that the shot noise term in Eq. \ref{eq:roman_shotnoise} differs from the standard shot noise term from \cite{Feldman:1994aa}, which uses $N_0^\mathrm{FKP} = \alpha (1+\alpha) \sum^{N_r}_{j=1} w_j^2. $The difference between shot noise formulations will be discussed further in Section \ref{sec:shotnoise}.

@@

@@

We also plot the $P_0(k)$ and $P_2(k)$ from the BOSS Data Release 12 CMASS data (\cmasscolor) in Figure \ref{fig:mockpk}. For BOSS DR12 CMASS, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber collisions. Each galaxy has a statistical weight determined by,

\begin{equation} \label{eq:weight}
w_{j, \mathrm{tot}} = w_{j, \mathrm{sys}} (w_{j, \mathrm{rf}} + w_{j, \mathrm{fc}} -1), 
\end{equation} 
(\citealt{Anderson:2012aa, Beutler:2014aa}), which are included in the object weights $w_j$ along with $w_{j, \mathrm{FKP}}$. The statistical weights are also included in the factor $\alpha$. So for the BOSS $P_0(k)$ and $P_2(k)$ calculations, $w_j = w_{j, \mathrm{tot}} \times w_{j, \mathrm{FKP}}$ and $\alpha' = \sum_{j=1}^{N_g} w_\mathrm{tot} / N_r$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% fiber collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Accounting for Fiber Collisions} \label{sec:fc_corr}
%Although the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:fc_pk} we demonstrate that at small scales its effects on the power spectrum are significant and dominate sample variance. In order to correct for this effect, in Section \ref{sec:dlospeak} we present an improved method to account for correlated fiber collided galaxies that uses the line-of-sight displacement between fiber collided pairs (Section \ref{sec:dlos}) and a shot-noise correction term in the power spectrum estimator that properly takes into account fiber collisions (Section \ref{sec:shotnoise}). In Section \ref{sec:fourier}, we present a complementary method that models the effect of fiber collisions on the power spectrum using an analytic estimate of the effect of fiber collisions on the 2PCF. 
\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
\caption{The ratio of $\overline{P_\mathrm{corr} (k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogs. The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}. We also plot the ratio of the sample variance to the true $\overline{P_\mathrm{true}(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) for comparison. Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber collisions for $k > 0.1 \; h/\mathrm{Mpc}$; however, neither method is able to constrain the systematic effects of fiber collisions significantly below the sample variance at $k > 0.2 \; h/\mathrm{Mpc}$.}\label{fig:fc_pk}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Effects of Fiber Collision on the Power Spectrum 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Nearest Angular Neighbor Method} \label{sec:fc_pk}
A common approach in accounting for fiber collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}), hereafter NN method. For galaxies without resolved spectroscopic redshifts due to fiber collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor. This method effectively assumes that all galaxies within the angular fiber collision scale ($< 62 \arcsec$ for BOSS) are correlated with one another. In other words, the method assumes that galaxies within the fiber collision angular scale reside in the same halo so displacing one of the galaxies and placing it on top of the other does not significantly alter the clustering statistics. One consequence of this method however is that galaxies within the angular fiber collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from their true position. For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$. Furthermore even for fiber-collided galaxies that reside in the same group or cluster, up-weighting the nearest neighbor ignores halo-scale line-of-sight displacements.

% Not only quantify the effect of fiber collisions, but the break down of the NN method for P(k) at high k. 
To precisely quantify the effect of fiber collisions on the power spectrum, in Figure \ref{fig:fc_pk}, we compare $P_0(k)$ and $P_2(k)$ measured using the NN method for mock catalogs with fiber collisions to the $P_0(k)$ and $P_2(k)$ measurements for mock catalogs without fiber collisions. The $P_0(k)$ measurements are made using Eq. \ref{eq:roman_p0k} with a standard FKP shot noise ($N_0^{FKP}$) rather than $N_0$ from Eq. \ref{eq:roman_shotnoise}, which is effectively just the standard power spectrum estimator from \cite{Feldman:1994aa}. $P_2(k)$ measurements are made using Eq. \ref{eq:roman_p2k}. 
\begin{itemize}
	\item Description of Figure \ref{fig:fc_pk} focusing on the scales where the NN method breaks down and quantifying the residuals. 
\end{itemize}

In order to correct for this effect, in following section we present an improved method to account for correlated fiber collided galaxies that uses the line-of-sight displacement between fiber collided pairs (Section \ref{sec:dlos}) and a corrected shot-noise correction term in the power spectrum estimator that properly takes into account fiber collisions (Section \ref{sec:shotnoise}).

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogs. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute the $d_{\mathrm{LOS}}$ distributions. The $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above). We focus on the peak of the distribution $-20 \; \mathrm{Mpc} < d_\mathrm{LOS} < 20 \;\mathrm{Mpc}$ (discussed in \ref{sec:dlos}).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DLOSPEAK METHOD 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{First Method} \label{sec:dlospeak}
% LOS DISPLACEMENT %%%%
\subsubsection{Line-of-Sight Displacement of Fiber Collided Pairs} \label{sec:dlos}
It is impossible to determine definitely from observed galaxy data whether individual fiber collided galaxies without resolved spectroscopic redshift are correlated or chance alignments. Fortunately, using the fiber collided pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the line-of-sight displacement of the fiber collided pairs and measure the fraction of pairs that are corrected and uncorrelated.

For simulated mock catalogs, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber collisions are post-processed after the simulated galaxy positions are generated. Redshift values are provided for all galaxies regardless of angular proximity and the fiber collisions imposed on the mock catalogs are represented through the galaxies' ``fiber collision weights" ($w_\mathrm{fc}$). So in a situation where only two galaxies are within the fiber collision angular scale, one galaxy (``the nearest neighbor") will have the fiber collision weight of both galaxies ($w_{\mathrm{fc}} = 2$), while the other has $w_\mathrm{fc} = 0$. Nonetheless, since we actually have redshifts of both fiber-collided pair galaxies in mock catalogs, we can model the correlated and uncorrelated fiber-collided pairs in order to better understand the effects of fiber collisions.

To determine whether or not fiber collided pairs are correlated, we examine the comoving line-of-sight displacement ($d_{\mathrm{LOS}}$) of fiber collided galaxy pairs. We calculate the $d_{\mathrm{LOS}}$ by taking the difference of the line-of-sight comoving distance from the resolved redshifts: 
\begin{equation}
d_{\mathrm{LOS}} = D_{\mathrm{C}} (z_1) - D_{\mathrm{C}} (z_2). 
\end{equation}
$D_{\mathrm{C}}(z)$ is the line-of-sight comoving distance at redshift $z$ (\citealt{Hogg:1999aa}). $z_1$ and $z_2$ represent the resolved redshifts of the two galaxies in the fiber collided pair.
